### 2014-10-21 PrivacyProtection-2014-09-09.tex
Added some TODOs. Renamed Crimial -> External.

\textbf{United Kingdom.} %TODO: HOW MUCH IS COPY PASTE FROM WIKIPEDIA?
The UK implements Directive 95/46 with the \emph{Data Protection Act 1998} (DPA).

@@

%% TODO %%

%* We follow Fried in defining privacy as the ability to control data about personal information.
%
%* What is the relation to legal aspects?
%
%* What should be personal information?
%
%* Use Seven Privacy Types be Friedewald, Finn and Wrigtht.

@@

The complexity of our systems and the variety of threads make a great number of counter measures plausible.
We approach this complexity with the aid of a general security analysis model developed in \cite{Grimm}.
We give a brief introduction to this model and perform a IT Security Analysis with respect to the privacy asset for our system.

@@

We follow the Reference Model for IT Security Analyis as described in \cite{Grimm}.
It supersedes earlier efforts by \cite{Avizienis}.

@@

The \emph{world view} contains all components describing the current state.
It consists of the following components:
\begin{itemize}
\item \textbf{Actors.}
All identifiable stakeholders of the system under study.
Typical actors include, users, developers, clients and criminals.

@@

In the example of the criminal-user-conflict, the criminal has to exploit a vulnerability, e.g. a weak password, to gain access to the private data abou the user.

@@

An example of a security requirement is that a given communication channel shall not be infringed by criminals.
\end{itemize}

@@

The \emph{concept view} is a realization of the the potential view of the system.
It specifies important interactions that require further planning.
It contains the following components:
\begin{itemize}
\item \textbf{Business Model.}
The plan to achieve business objectives.

@@

\item \textbf{Security Measures.}
It describes a plan of sufficient measures to secure the intended interactions and to aviod the unintended interactions.
Each security measure targets a vulnerability of the system in order to reduce a risk for a certain thread.
\end{itemize}

@@

This section describes the human actors previously introduced within the IT system architecture (\ref{subsubsection:it-systems}).
Also the additional actor \textit{Criminal} is introduced as an external person with harmful intentions.

@@

\textbf{Criminal.}
Criminals are persons who do not have privileged access to the IT systems,
and are willing to break laws and norms in order to promote their interests.

For example they want to obtain access to critical systems to steal sensitive data or to get the system under their control.
Controlled systems could be leased as part of a bot net.
Stolen data could simply be sold as is or used for illegitimate purposes, e.g. spam or phishing attacks - or excessive data mining.

@@

Criminals could want to harm or destroy the systems in order to damage the reputation of local authorities (politicians or other officials) or to make a political statement of their own.

Another possible motivation for criminal activities could be social appreciation.
A hacker could attack critical infrastructure just to prove his skills.

In short, Criminals are interested in
\begin{itemize}
\item financial profit
\item political activism
\item social standing.
\end{itemize}

@@

\input{./figures/LG-Conflicts-Of-Interests}

\textbf{System Complexity vs Privacy of the Citizen.}
System Providers offer a service to local authorities, which is to provide and maintain the IT system.
This system shall produce business intelligence, so that local authorities can improve their public services.
This task in it self has a high technical complexity and is the sole asset with financial return for system provider.

\textbf{System Complexity vs Privacy:}
System Providers offer a service to Local Authorities, which is to provide and maintain a monitoring and mining system, e.g. for public mobility.
This system shall produce business intelligence, so that Local Authorities can improve their public services.
This task in it self has a high technical complexity and is the sole asset with financial return for System Providers.
However, this task operates on privacy sensitive data provided by monitored Citizens.
In order to ensure their privacy, System Provider would have to implement additional mechanisms, which allow Citizens to exercise control of their data.
This will not only raise the complexity of the monitoring and mining system, System Providers also have to layout the complexity in a comprehensible manner.
To effectively enable Citizens to preserve their privacy, they need to know what happens with their data.

@@

\textbf{Financial Profit of Criminal vs Privacy.}
Criminals can gain financial profit from stealing privacy sensitive data.
For example by selling raw contact information to advertisers or by selling mined data to insurance companies, or intermediaries like scoring companies.
In such cases, citizens lose complete control over their data.

\textbf{Financial Profit of Criminal vs Reputation of System Providers.}
Criminals have various business models as optional foundation for attacks on System Providers.
For instance, they can try to invade the infrastructure for e-espionage reasons, to get control over servers to create a bot-net or to steal user data.
All these approaches are motivated by financial interests.
Gathered information can be sold, zombie servers can be leased.

@@

\textbf{Political Activism vs Reputation of Local Authority.}
Besides monetary reasons, Criminals can be motivated by political reasons to attack the monitoring and mining system.
Criminals can break the system to make a political statement of their own,
or they can steal user data to prove the system insecure.
Both would harm the reputation of local authorities, who endangered the privacy of the citizens.

@@

\textbf{Unencrypted Data Transmission:}
The proposed monitoring and mining system uses HTTP to exchange data between the Sensor Collector, the Data Center and the Report Tool.
Per default, HTTP is a clear text protocol.
This means, one can intercept the connection and read all sensitive information, which is send between the components.
That is: passwords, raw sensor data and data mining results

\textbf{Inadequate Access Rules:}
The proposed IT system infrastructure has various accesses to privacy sensitive data.
System Provider staff has access to Data Center hardware and software like databases, web-servers and other inspection tools.
Local Authority staff has access to the Report Tool.
This all enables staff members to have potential access to privacy sensitive information.
Those accesses have to be secured against unauthorized third parties, e.g. Criminals.
Moreover, we need to ensure that no single person has to many access rights.
For example, a system administrator should not be able to secretly download the whole database on a flash-drive.

\textbf{Insufficiently Secured Infrastructure:}
The proposed monitoring system consists of many hardware and software components, each with its own concrete weaknesses.
For instance, operating systems can be outdated or not subject to frequent updates or virus scans.
Web-applications can be carelessly implemented and not protected against SQL-Injections or Cross-Site-Scripting attacks.
Databases can be ill-configured, so that access from outside the system is possible.
All those weak points can be subject to various known exploit techniques.

\textbf{Unaware Monitoring Subjects:}
We define privacy as one's ability to control information about oneself. 
In order to do that, monitored subjects need to know, that they are monitored, who monitors them, what information is recorded and for what purposes.
Subjects who are not aware of these things cannot effectively preserve control and thus lose their privacy.

@@

%\includegraphics{../diagrams/png/sensor-privacy-matrix.png}
\input{./figures/LG-Sensor-Privacy-Matrix}
\input{./figures/LG-Implicit-Sensor-Privacy-Matrix}

>>>>

\textbf{United Kingdom.}
The UK implements Directive 95/46 with the \emph{Data Protection Act 1998} (DPA).

@@

%TODO: Iterate Section. Exmplain Triangular Relationship:
- Subject
- Trusted Person
- Third Party which shall NOT obtain sensitive information.

@@

The complexity of our systems and the variety of threads make a great number of counter measures plausible.
We approach this complexity with the aid of a general security analysis model developed in \cite{Grimm:ItSecRefModel}.
We give a brief introduction to this model and perform a IT Security Analysis with respect to the privacy asset for our system.

@@

We follow the Reference Model for IT Security Analyis as described in \cite{Grimm:ItSecRefModel}.
It supersedes earlier efforts by \cite{Avizienis}.

@@

The \emph{world view} contains all components describing the current state.
It consists of the following components:
\begin{itemize}
\item \textbf{Actors.}
All identifiable stakeholders of the system under study.
Typical actors include, users, developers, clients and externals.

@@

In the example of the criminal-user-conflict, the criminal has to exploit a vulnerability, e.g. a weak password, to gain access to the private data about the user.

@@

An example of a security requirement is that a given communication channel shall not be infringed by externals.
\end{itemize}

@@

The \emph{concept view} is a realization of the potential view of the system.
It specifies important interactions that require further planning.
It contains the following components:
\begin{itemize}
\item \textbf{Business Model.}
The plan to achieve business objectives.

@@

\item \textbf{Security Measures.}
It describes a plan of sufficient measures to secure the intended interactions and to avoid the unintended interactions.
Each security measure targets a vulnerability of the system in order to reduce a risk for a certain thread.
\end{itemize}

@@

This section describes the human actors previously introduced within the IT system architecture (\ref{subsubsection:it-systems}).
Also the additional actor \textit{External} is introduced as a person with no special access rights.

@@

%TODO:
- Nondisclosure of sensitive information to peers of the citizen.

\textbf{External.}
Externals are persons who do not have privileged access to the IT systems, and are willing to break laws, security constrains and norms in order to promote their interests.

If the external is in some kind of relationship to the citizen, like a friendship or business partnership, the external can have a direct interest in gaining information about the citizen in order to increase their power.

Another common interest of an external is financial profit. For example they want to obtain access to critical systems to steal sensitive data or to get the system under their control.
Controlled systems could be leased as part of a bot net.
Stolen data could simply be sold as is or used for illegitimate purposes, e.g. spam or phishing attacks - or excessive data mining.

@@

Externals could want to harm or destroy the systems in order to damage the reputation of local authorities (politicians or other officials) or to make a political statement of their own.

Another possible motivation for external  activities could be social appreciation.
A hacker could attack critical infrastructure just to prove his skills.

In short, externals are interested in
\begin{itemize}
\item increase power over citizen
\item financial profit
\item political activism
\item social standing.
\end{itemize}

@@

\input{./figures/LG-Conflicts-Of-Interests}
%TODO: Adapt Figure

\textbf{System Complexity vs Privacy.}
System Providers offer a service to Local Authorities, which is to provide and maintain a monitoring and mining system, e.g. for public mobility.
This system shall produce business intelligence, so that Local Authorities can improve their public services.
This task in it self has a high technical complexity and is the sole asset with financial return for System Providers.
However, this task operates on privacy sensitive data provided by monitored Citizens.
In order to ensure their privacy, System Provider would have to implement additional mechanisms, which allow Citizens to exercise control of their data.
This will not only raise the complexity of the monitoring and mining system, System Providers also have to layout the complexity in a comprehensible manner.
To effectively enable Citizens to preserve their privacy, they need to know what happens with their data.

@@

\textbf{Power of External vs. Privacy.}
Externals which are in a social relation to the citizen can have an interest in obtaining further information in order to gain power.
In the most simplistic example this could be a man wanting monitor the activities of his spouse.
Another example is a Government spying on it's citizens in order to suppress opposition.
An additional twist in the last example is, that there can be legal regulations that require the service provider to support the Governments invasion of the citizens privacy.

\textbf{Financial Profit of External vs Privacy.}
Externals can gain financial profit from stealing privacy sensitive data.
For example by selling raw contact information to advertisers or by selling mined data to insurance companies, or intermediaries like scoring companies.
In such cases, citizens lose complete control over their data.

\textbf{Financial Profit of External vs Reputation of System Providers.}
Externals have various business models as optional foundation for attacks on System Providers.
For instance, they can try to invade the infrastructure for e-espionage reasons, to get control over servers to create a bot-net or to steal user data.
All these approaches are motivated by financial interests.
Gathered information can be sold, zombie servers can be leased.

@@

\textbf{Political Activism vs Reputation of Local Authority.}
Besides monetary reasons, externals can be motivated by political reasons to attack the monitoring and mining system.
Externals can break the system to make a political statement of their own,
or they can steal user data to prove the system insecure.
Both would harm the reputation of local authorities, who endangered the privacy of the citizens.

@@

\textbf{Insecure Infrastructure.}
The proposed monitoring system consists of many hardware and software components, each with its own concrete weaknesses.
For instance, operating systems can be outdated or not subject to frequent updates or virus scans.
Web-applications can be carelessly implemented and not protected against SQL-Injections or Cross-Site-Scripting attacks.
Databases can be ill-configured, so that access from outside the system is possible.
All those weak points can be subject to various known exploit techniques.

\textbf{Insecure Data Transmission.}
The proposed monitoring and mining system uses HTTP to exchange data between the Sensor Collector, the Data Center and the Report Tool.
Per default, HTTP is a clear text protocol.
This means, one can intercept the connection and read all sensitive information, which is send between the components.
That is: passwords, raw sensor data and data mining results

\textbf{Unhappy Employees.} Susceptible for social engineering.
%TODO: Add description

\textbf{Inadequate Access Rules.}
The proposed IT system infrastructure has various accesses to privacy sensitive data.
System Provider staff has access to Data Center hardware and software like databases, web-servers and other inspection tools.
Local Authority staff has access to the Report Tool.
This all enables staff members to have potential access to privacy sensitive information.
Those accesses have to be secured against unauthorized third parties.
Moreover, we need to ensure that no single person has to many access rights.
For example, a system administrator should not be able to secretly download the whole database on a flash-drive.

\textbf{Unaware Monitoring Subjects.}
We define privacy as one's ability to control information about oneself. 
In order to do that, monitored subjects need to know, that they are monitored, who monitors them, what information is recorded and for what purposes.
Subjects who are not aware of these things cannot effectively preserve control and thus lose their privacy.

%TODO
- No Privacy Policy
- No Information about Processing, Access rules, 3rd party disclosure

@@

%\includegraphics{../diagrams/png/sensor-privacy-matrix.png}
\input{./figures/LG-Sensor-Privacy-Matrix}
%\input{./figures/LG-Implicit-Sensor-Privacy-Matrix}
